---
title: "CSPS microdata training"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(gradethis)
library(learnr)
library(tidyverse)

tutorial_options(exercise.checker = gradethis::grade_learnr)
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, error = FALSE)

path <- "https://github.com/matt-dray/cspstrain/blob/master/data/csps-synth-small.RDS"
data <- readRDS(path)
```


## Introduction

### What this is and isn't

This tutorial is an introduction to dealing with Civil Service People Survey (CSPS) microdata using R.

Throughout the tutorial you'll be asked to type R code into boxes.

The tutorial isn't intended as a proper introduction to R, though it does assume that you're a beginner.

### Using this tutorial

On the left is the navigation bar. You can jump to different sections of the tutorial from here.

Beneath it are the words 'Start over'. If you click here then the tutorial will be completely reset.

The code execution blocks say 'Code' in the top-left corner. They will typically have three buttons:

* the blue 'Run Code' button executes the code you've written and displays the outputs underneath the box
* 'Start Over' returns the box to its initial state
* clicking 'Hint' will show a pop-up with information to help you

Below is a code box example. Type 'hello' (all lowercase) between the quotation marks and press 'Run Code' to print your statement.

```{r hello, exercise = TRUE}
print("")
```

```{r hello-solution}
print("hello")
```

```{r hello-check}
# grade_result(
#   pass_if(~identical(.result, "Hello"), "Hello to you too.")
# )

grade_code("Hello to you too.")
```


### A note on the data

The data set used in this package isn't real. None of the rows represent results from real respondents.

Instead, the data set is _synthetic_. This means that the distribution of results within any given variable is representative of the real data set, but none of the rows represent a real person's responses.

## Look

I've already loaded the data set for you. It's available as a data frame named `data`. You can view it by typing 'data' in the box below and clicking the blue 'Run' button in the upper right corner of the box.

```{r print, exercise=TRUE}

```

You'll see that the data set has a number of rows and columns containing data. The absence of data is denoted as `NA`.

It's often a bit much to print _all_ the data at once. You can supply the name of the data frame to the `head()` function to limit the output to just the first few rows. Try that now.

```{r head, exercise=TRUE}

```

If you're having trouble, you can click the hint button for advice.


```{r glimpse, exercise=TRUE}

```

```{r nrow, exercise=TRUE}

```

```{r length, exercise=TRUE}

```

## Wrangle

## Derive

## Plot
